Interactive effects of drought and habitat fragmentation on vital rates of an understory tropical plant

### 2021-02-09 analysis/paper/paper.Rmd
worked on survival results section

size: p \< 0.001 (figure = surv_cf_size.png)

SPEI: p \< 0.001 (figure = surv_cf_spei.png)

Lags 6-0 (Aug--Feb) and 20-15 (Jun--Nov) show reduced survival with drought.
Lags 14-7 (Dec - Jul) and 26-21 (Dec-May) show increased survival with drought.
Lag 36-33 (Feb - May) shows quadratic relationship with increased survival in dry and wet conditions (this seems like it's gotta be spurious).

size: p \<0.001 (figure = surv_1ha_size.png)

plot: p = 0.258

SPEI: p \< 0.001 (figure = surv_1ha_spei.png)

Crossbasis is very flat with essentially no effect of SPEI beyond 6 months lag.
Recent SPEI has bimodal effect with both low and high values reducing survival.

**Question**: Currently the figures are expected values for the average plant across both plots.
This makes it look like survival is a lot higher in 1-ha fragments when in reality survival is exactly the same (0.95) because plants are smaller in 1-ha fragments.
Should these plots instead be for an average sized plant within the habitat type?

@@

Plants were on average larger in continuous forest compared to 1-ha fragments.
In continuous forest, plants had an average of 2.91 shoots and were on average 40.6 cm tall with an average size (shoots $\times$ height) of 150.
In 1-ha fragments, plants had 2.53 shoots on average and a mean height of 36.2 cm and a mean size of 115.

>>>>

Log transformed plant size had a significant effect on survival in both continuous forest and 1-ha fragments (both p \< 0.001).
Survival probability of large plants approached 1, but this high survival rate was reached at a smaller size for plants in continuous forest compared to fragments (Figure \_\_\_ <!--# might be good to plot both curves on same graph -->).
Survival of the smallest plants was higher in 1-ha fragments, but the confidence intervals still overlapped the fitted values for continuous forest.

Drought history had a significant effect on survival in both habitats (P \< 0.001), but the shape of the crossbasis surface differed.
For 1-ha fragments, recent SPEI values had the strongest effect on survival with the highest survival near SPEI of 0 and decreasing survival in both drier and wetter conditions (Figure \_\_\_).
In continuous forest, recent SPEI had a weaker effect with only SPEI values less than -1 producing slightly reduced survival probabilities.
However, SPEI at a lag time of 15--20 months, corresponding to June--October of the previous year, also effected survival probabilities.
Lower SPEI (drought) 15--20 months prior to census was associated with reduced survival and higher SPEI at these lag times was associated with higher survival.
Plants in both continuous forest and 1-ha fragments showed an increase in survival probability with very high (wet) SPEI values at a lag time of 36 months.
However, only the first year of census data (1999) had an SPEI value greater than 2 within 36 months in the past, and although there were plants that did not survive this initial census, it may not be representative of a true survival process <!--# Emilio: let's talk about this. Maybe I should remove this year from the analysis for survival? -->

The random effect of plot was significant for continuous forest ( p \< 0.001), but not for 1-ha fragments (p = 0.258 <!--# double-check -->)

@@

Plants were on average larger in continuous forest compared to 1-ha fragments.
In continuous forest, plants had an average of 2.91 shoots and were on average 40.6 cm tall with an average size (shoots $\times$ height) of 150.
In 1-ha fragments, plants had 2.53 shoots on average and a mean height of 36.2 cm and a mean size of 115.
Log transformed size in year t was a significant predictor of log transformed size in year t+1 (p \< 0.001) and the relationship was close to linear for both continuous forest (edf = ) and 1-ha fragments (edf = ).
